\pkg{sdmTMB}: An \proglang{R} Package for Fast, Flexible, and User-Friendly Generalized Linear Mixed Effects Models with Spatial and Spatiotemporal Random Fields

### 2024-06-01 doc/paper-jss/sdmTMB-paper.Rnw
Drop first 'we note'
Drop 2nd we note

% We omit example code for Moran's I calculation for brevity but include it in the code supplement.
\added{
We see strong evidence for spatial autocorrelation for the model without a random field (p $<$ 0.01) but a lack of evidence for spatial correlation after including a random field (p $>$ 0.01) suggesting that residual spatial autocorrelation is alleviated by including the random field.
We note that the specific p-value is dependent on the seed due to the randomization in the randomized quantile residuals.
}

@@

\added{
\Rev{A1}We note that caution is warranted in performing model selection via marginal AIC for models involving penalized smoothing (spatial or otherwise) \citep[e.g.][]{greven2010, safken2021}.
In marginal AIC calculation, the degrees of freedom is based on the number of fixed effects and does not account for the degree of random effect penalization as conditional AIC would.
Methods to estimate effective degrees of freedom for similar models were recently demonstrated in \citet{thorson2024cAIC}, but are not yet included in \sdmTMB.
}

@@

\input{../../../sdmTMB-paper-response/response2}

>>>>

% We omit example code for Moran's I calculation for brevity but include it in the code supplement.
\added{
We see strong evidence for spatial autocorrelation for the model without a random field (p $<$ 0.01) but a lack of evidence for spatial correlation after including a random field (p $>$ 0.01) suggesting that residual spatial autocorrelation is alleviated by including the random field.
The specific p-value is dependent on the seed due to the randomization in the randomized quantile residuals.
}

@@

\added{
\Rev{A1}Caution is warranted in performing model selection via marginal AIC for models involving penalized smoothing (spatial or otherwise) \citep[e.g.][]{greven2010, safken2021}.
In marginal AIC calculation, the degrees of freedom is based on the number of fixed effects and does not account for the degree of random effect penalization as conditional AIC would.
Methods to estimate effective degrees of freedom for similar models were recently demonstrated in \citet{thorson2024cAIC}, but are not yet included in \sdmTMB.
}

@@

% \input{../../../sdmTMB-paper-response/response2}
